---
title: "Recalculating FIS scores with Updated data"
output: html_document
---


## Compare version 2015 vs 2019 FIS data

**Using the original functions.R file and same Pressures/Resilinece Layers**

- Recalculating BHI scores using everything from 2015 assessment except revised Fisheries data
- Replacement datasets for fis_bbmsy, fis_ffmsy, fis_landings

```{r recalculating with same function v2015 data, echo=FALSE, include=FALSE}
library(tidyverse)
dir <- file.path(here::here(), "baltic2015")

## original v2015 functions of v2019 with the constant v2015 0.87 penalty for eastern cod
file.copy(file.path(dir, "compare", "functions2015.R"), file.path(dir, "conf", "functions.R"), overwrite = TRUE)
# file.copy(file.path(dir, "functions", "functions2019_constantPenalty.R"), file.path(dir, "conf", "functions.R"), overwrite = TRUE) 


## use 2015 layers and layers.csv to calculate scores
file.copy(file.path(dir, "compare", "layers2015.csv"), file.path(dir, "layers.csv"), overwrite = TRUE)
## for first calculation, need to copy bhi-1.0-archive baltic2015 layers
library(httr)
req <- GET("https://api.github.com/repos/OHI-Science/bhi-1.0-archive/git/trees/draft?recursive=1")
stop_for_status(req)
filelist <- unlist(lapply(content(req)$tree, "[", "path"), use.names = FALSE) %>% 
  grep(pattern = "baltic2015/layers/", value = TRUE) %>% 
  str_extract("/[a-zA-Z0-9_-]+.csv|/[a-zA-Z0-9_-]+$") %>% 
  str_remove_all(".csv")
lyrcsv2015 <- read_csv(file.path(dir, "compare", "layers2015.csv"))
dir.create(file.path(dir, "layers"))
lapply(
  c(
    intersect(lyrcsv2015$filename, str_remove(filelist, "/") %>% paste0(".csv")), 
    "eco_trend_scores_BHI2015.csv" # random capitalization causes issue...
  ),
  function(x){
    read_csv(paste0("https://raw.githubusercontent.com/OHI-Science/bhi-1.0-archive/draft/baltic2015/layers/", unlist(x))) %>% 
      write_csv(file.path(dir, "layers", unlist(x) %>% str_replace_all("_BHI2015", "_bhi2015")))
  }
)
source(file.path(dir, "calculate_scores.R"))
scores2015 <- read.csv(file.path(dir, "scores.csv"))

## compare to the archived version to confirm it's the same
# scores2015_archive <- read.csv(file.path("../baltic2015/scores.csv"))
# compare_scores <- cores2015 %>%
#   left_join(scores2015_archive, by = c("goal", "dimension", "region_id")) %>%
#   mutate(diffs = score.x-score.y)
# summary(compare_scores$diffs)
```


```{r recalculating with same function v2019  data, echo=FALSE, include=FALSE}
## now substitute new FIS goal layers from 2019 data prep
## copy these over from the bhi-prep v2019 layers folder
req <- GET("https://api.github.com/repos/OHI-Science/bhi-prep/git/trees/master?recursive=1")
stop_for_status(req)
filelist <- unlist(lapply(content(req)$tree, "[", "path"), use.names = FALSE) %>% 
  grep(pattern = "layers/v2019/", value = TRUE) %>% 
  str_extract("[a-z0-9_]+.csv")
lapply(
  filelist,
  function(x){
    read_csv(paste0("https://raw.githubusercontent.com/OHI-Science/bhi-prep/master/layers/v2019/", unlist(x))) %>% 
      rename(rgn_id = region_id) %>% 
      write_csv(file.path(dir, "layers", unlist(x)))
  }
)
new_fis_lyrs <- c("fis_ffmsy_bhi2019.csv", "fis_bbmsy_bhi2019.csv", "fis_landings_bhi2019.csv")
file.exists(file.path(dir, "layers", new_fis_lyrs))

lyrs_csv_fis2019 <- read_csv(file.path(dir, "compare", "layers2015.csv")) %>%
  mutate(
    filename = ifelse(
      layer == "fis_bbmsy", "fis_bbmsy_bhi2019.csv",
      ifelse(layer == "fis_ffmsy", "fis_ffmsy_bhi2019.csv",
             ifelse(layer == "fis_landings", "fis_landings_bhi2019.csv", filename)
      )
    ),
    fld_val_num = ifelse(
      layer == "fis_bbmsy", "value",
      ifelse(layer == "fis_ffmsy", "value", fld_val_num)
    ),
    fld_value = ifelse(
      layer == "fis_bbmsy", "value",
      ifelse(layer == "fis_ffmsy", "value", fld_value)
    ))
write_csv(lyrs_csv_fis2019, file.path(dir, "layers.csv"))
source(file.path(dir, "calculate_scores.R"))
scores_w_fis2019 <- read.csv(file.path(dir, "scores.csv"))
```


```{r compare scores2015 and scores_w_fis2019 version 2015 goal function, echo=FALSE, include=FALSE}
## joing scores tables and view summaries
compare_scores <- scores_w_fis2019 %>%
  rename(score2019 = score) %>%
  left_join(
    rename(scores2015, score2015 = score),
    by = c("goal", "dimension", "region_id")
    ) %>%
  mutate(diffs = score2015-score2019)

summary(compare_scores$diffs)
## but differences only in FIS, FP, and Index as expected
summary(filter(compare_scores, !goal %in% c("FIS", "FP", "Index"))$diffs)

## some plots to visualize how new data shifted scores
## old minus revised scores so positive diffs mean revised scores are lower:
# summary(filter(compare_scores, goal == "FIS")$diffs)

compareFP <- filter(compare_scores, goal %in% c("FIS", "FP", "Index"), region_id %in% 1:42)
hist <- ggplot(filter(compareFP, dimension %in% c("status", "future", "score"))) +
  geom_histogram(aes(diffs)) +
  facet_grid(vars(goal), vars(dimension)) +
  labs(x = "score differences (2015 scores minus scores revised with 2018 data, for yr 2014)") +
  theme_bw()

trends_plot <- ggplot(filter(compare_scores, goal == "FIS", dimension == "trend")) + 
  # geom_ribbon(aes(x = region_id, ymin = score2019, ymax = score2015), alpha = 0.1) +
  # geom_point(aes(region_id, score2015), color = "mediumorchid", size = 0.8) +
  # geom_point(aes(region_id, score2019), color = "darkslategrey", size = 0.8) +
  geom_crossbar(
    aes(x = region_id, y = score2019, ymin = score2019, ymax = score2015), 
    alpha = 0.1, color = "darkslategrey", fill = "mediumorchid"
  ) +
  labs(x = NULL, y = "trend scores with 2015 (purple) and 2019 (green) FIS data") +
  theme_bw()

compare_plot <- ggplot(filter(compareFP, dimension %in% c("status", "future", "score"))) +
  geom_point(aes(score2015, score2019, color = region_id), alpha = 0.6, size = 1.5) +
  geom_abline(slope = 1, intercept = 0) +
  facet_grid(vars(goal), vars(dimension)) +
  labs(x = "scores calculated with old dataset", y = "scores calculated with updated FIS data") +
  theme_bw()
# compare_plot
# plotly::ggplotly(compare_plot)
```

<br>

Table with the results, just `status` dimension for FIS goal and BHI regions not EEZs or Subbasins:

```{r view result}
DT::datatable(
  filter(compare_scores, goal == "FIS", dimension == "status", region_id %in% 1:42), 
  class = 'cell-border stripe', 
  options = list(pageLength = 42)
)
```

## Histograms

```{r, warning=FALSE, message=FALSE}
hist
plotly::ggplotly(trends_plot)
```


### Scores calculated with 2015 vs 2019 FIS datasets 

**(F/FMSY, B/BMSY, Landings)**

```{r}
plotly::ggplotly(compare_plot)
```

<br>

## Compare 2015 vs 2019 data using updated `FIS` function

```{r recalculating with slightly revised FIS functions, include=FALSE}
## write v2019 functions to conf folder to use in calculation
file.copy(file.path(dir, "compare", "functions2019.R"), file.path(dir, "conf", "functions.R"), overwrite = TRUE)

## create layers.csv tables with and extra entry for the cod penalty layer
cod_penalty_lyr <- data.frame(
  targets = "FIS", layer = "fis_cod_penalty", name = "Cod Condition Penalty Factor", 
  description = "Proportion of Cod 20-40cm with Fultons K less than 0.8", 
  fld_value = "penalty_factor", units = "proportion", 
  filename = "fis_cod_penalty_bhi2019.csv", clip_n_ship_disag = NA, clip_n_ship_disag_description = NA, 
  layer_gl = NA, path_in = NA, rgns_in = NA, fld_id_num = "rgn_id", fld_id_chr = NA, 
  fld_category = NA, fld_year = NA, fld_val_num = "penalty_factor", fld_val_chr = NA, 
  file_exists = NA, year_min = NA, year_max = NA, 
  val_min = NA, val_max = NA, val_0to1 = NA, flds_unused = NA, 
  flds_missing = NA, rows_duplicated = NA, num_ids_unique = NA, data_na = NA
)

## with v2015 data
## recalculate scores with updated function and version 2015 (origial) FIS data
rbind(read_csv(file.path(dir, "compare", "layers2015.csv")), cod_penalty_lyr) %>% 
  write_csv(file.path(dir, "layers.csv"))
source(file.path(dir, "calculate_scores.R"))
scores2015_reviseFun <- read.csv(file.path(dir, "scores.csv"))

## with v2019 data
## recalculate scores with updated function and version 2019 (revised) FIS data
rbind(lyrs_csv_fis2019, cod_penalty_lyr) %>% 
  write_csv(file.path(dir, "layers.csv"))
source(file.path(dir, "calculate_scores.R"))
scores2019_reviseFun <- read.csv(file.path(dir, "scores.csv"))
```

```{r v2015 and v2019 datasets differences when using revised FIS function, include=FALSE}
## join v2015 and v2019
compare_final <- scores2019_reviseFun %>%
  rename(score2019 = score) %>%
  left_join(
    rename(scores2015_reviseFun, score2015 = score),
    by = c("goal", "dimension", "region_id")
    ) %>%
  mutate(diffs = score2015-score2019) %>% 
  filter(
    goal %in% c("FIS", "FP", "Index"),
    dimension %in% c("status", "future", "score", "trend"), 
    region_id %in% 1:42
  )

## comparing score differences for v2015 vs v2019 functions
compare_compare <- compare_final %>% # compares data using v2019 function
  rename(
    score2019_newFUN = score2019, 
    score2015_newFUN = score2015, 
    diffs_newFUN = diffs
  ) %>% 
  left_join(
    compare_scores, # compares data using v2015 function
    by = c("goal", "dimension", "region_id")
  ) %>% 
  mutate(diffs2 = diffs_newFUN-diffs)
# hist(compare_compare$diffs2)
```

```{r make plots of diffs using revised v2019 FIS function, include=FALSE}
compareFUNS_plot <- ggplot(
  compare_compare %>% 
    select(region_id, diffs_newFUN, diffs) %>% 
    rename(
      `differences with new FIS fun` = diffs_newFUN,
      `differences with v2015 FIS fun` = diffs
    ) %>% 
    gather("tst", "diff", -region_id)) + 
  geom_histogram(aes(diff), binwidth = 1) + 
  facet_grid(vars(tst))

compareFP_final <- filter(compare_final, goal %in% c("FIS", "FP", "Index"), region_id %in% 1:42)
compare_plot_final <- ggplot(compareFP_final %>% filter(dimension %in% c("status", "future", "score"))) +
  geom_point(aes(score2015, score2019, color = region_id), alpha = 0.6, size = 1.5) +
  geom_abline(slope = 1, intercept = 0) +
  facet_grid(vars(goal), vars(dimension)) +
  labs(x = "scores calculated with old dataset", y = "scores calculated with updated FIS data") +
  theme_bw()

hist_final <- ggplot(filter(compareFP_final, dimension %in% c("status", "future", "score"))) +
  geom_histogram(aes(diffs)) +
  facet_grid(vars(goal), vars(dimension)) +
  labs(x = "score differences (2015 scores minus scores revised with 2018 data, for yr 2014)") +
  theme_bw()

trends_plot_final <- ggplot(filter(compare_final, goal == "FIS", dimension == "trend")) + 
  # geom_ribbon(aes(x = region_id, ymin = score2019, ymax = score2015), alpha = 0.1) +
  # geom_point(aes(region_id, score2015), color = "mediumorchid", size = 0.8) +
  # geom_point(aes(region_id, score2019), color = "darkslategrey", size = 0.8) +
  geom_crossbar(
    aes(x = region_id, y = score2019, ymin = score2019, ymax = score2015), 
    alpha = 0.1, color = "darkslategrey", fill = "mediumorchid"
  ) +
  labs(x = NULL, y = "trend scores with 2015 (purple) and 2019 (green) FIS data") +
  theme_bw()
```

Plot comparing score results with v2015 vs v2019 `FIS` datasets

Looks about the same as above...

```{r comparisons plots ver2015 data vs ver2019}
plotly::ggplotly(compare_plot_final)
```

**Histograms show distributions of differences between scores calculated using version 2015 and v2019 data** 

The histograms are quite similar; changes in the `FIS` score calculation function generally result in much smaller differences than the underlying FIS datasets.

```{r differences with functions vs data changes}
compareFUNS_plot
```

**Data Table**
```{r datatable for final comparison}
DT::datatable(
  filter(compare_final, dimension == "status", goal == "FIS"), 
  class = 'cell-border stripe', 
  options = list(pageLength = 42)
)
```


```{r more plots to match first section, warning=FALSE, message=FALSE}
hist_final
plotly::ggplotly(trends_plot_final)
```


### Do these differences make sense?

Regions 11, 12, 13, 16 recieve better scores with 2019 data because of inclusion of Eastern cod (which despite poor condition, is high scoring because of decent B/BMSY and F/FMSY)

Regions 3, 4, 7-10, (ICES subdivision 22) contain only scores for Western not Eastern cod stock. The same goes for BHI 5&6 The Sound ie ICES 23, but `her_3a22` for some reason is missing from `ffmsy` data for 5 and 6 for year 2014, resulting in higher scores for these 2 regions.

In BHI Regions 37-42 scores decreased with the 2019 data, because in the 2019 version of the prepared data, Eastern cod are not included. Herring in those regions have biomass much above the MSY value, and though mortality is also well above 1, BHI penalizes for underfishing-- something to consider when setting the F and B score parameters, though these parameters need to work for all stocks...


```{r reasons for differences, eval=FALSE, include=FALSE}
lapply(
  list("fis_bbmsy_bhi2019.csv", "fis_bbmsy_bhi2015.csv", 
    "fis_ffmsy_bhi2019.csv", "fis_ffmsy_bhi2015.csv", 
    "fis_landings_bhi2019.csv", "fis_landings_bhi2015.csv"
  ), function(x){
    View(read_csv(file.path(dir, "layers", unlist(x))), title = str_extract(unlist(x), "[a-z0-9_]+"))
    assign(
      str_extract(unlist(x), "[a-z0-9_]+"), 
      read_csv(file.path(dir, "layers", unlist(x))), 
      envir = .GlobalEnv    
    )
  }
)
```

<br>

**Data for Eastern cod in the version 2015 dataset only go to year 2012...**

Recalculate everything again assiging 2012 eastern cod data for 2014 scenario
Re-run relevant chunks using scores2015_reviseFun above: summary and plot chunks i.e. 3-6, 8-13...

```{r recalculate everything again assiging 2012 eastern cod data for 2014 scenario, echo=FALSE, include=FALSE}
read_csv(file.path(dir, "layers", "fis_bbmsy_bhi2015.csv")) %>% 
  mutate(year = ifelse(year == 2012 & stock == "cod_2532", 2014, year))%>% 
  write_csv(file.path(dir, "layers", "fis_bbmsy2015_codE2012.csv"))

read_csv(file.path(dir, "layers", "fis_ffmsy_bhi2015.csv")) %>% 
  mutate(year = ifelse(year == 2012 & stock == "cod_2532", 2014, year)) %>% 
  write_csv(file.path(dir, "layers", "fis_ffmsy2015_codE2012.csv"))

layers2015_codE2012 <- read_csv(file.path(dir, "compare", "layers2015.csv")) %>% 
  mutate(filename = ifelse(layer == "fis_bbmsy", "fis_bbmsy2015_codE2012.csv", filename)) %>% 
  mutate(filename = ifelse(layer == "fis_ffmsy", "fis_ffmsy2015_codE2012.csv", filename))

## recalculate scores with v2015 function 
## and v2015 data with eastern cod in 2014 taking 2012 values
file.copy(file.path(dir, "compare", "functions2015.R"), file.path(dir, "conf", "functions.R"), overwrite = TRUE)
write_csv(layers2015_codE2012, file.path(dir, "layers.csv"))
source(file.path(dir, "calculate_scores.R"))
scores2015 <- read.csv(file.path(dir, "scores.csv")) # now re-run relevant chunks using scores2015 above

## recalculate scores with v2019 function 
## and v2015 data with eastern cod in 2014 taking 2012 values
file.copy(file.path(dir, "compare", "functions2019.R"), file.path(dir, "conf", "functions.R"), overwrite = TRUE)
write_csv(rbind(layers2015_codE2012, cod_penalty_lyr), file.path(dir, "layers.csv")) # need cod penalty layer
source(file.path(dir, "calculate_scores.R"))
scores2015_reviseFun <- read.csv(file.path(dir, "scores.csv"))

## now re-run relevant chunks using scores2015_reviseFun above...
## summary and plot chunks i.e. 3-6, 8-13, no 'source(calculate_scores.R)' chunks...
```

<br>
