---
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
source(file.path(here::here(), "R", "setup.R"))
short_goal_web <- file.path(bhiprep_gh_raw, "master", "ref", "goal_summaries") # bhiprep_gh_raw defined in setup.R
# short_goal_web <- file.path(
#   "https://raw.githubusercontent.com/OHI-Science/bhi-1.0-archive",
#   "draft/baltic2015", 
#   "conf", "web", "goals"
# )

## this document links to the bhi-prep github repo, using 
layers_web <- "http://ohi-science.org/bhi/layers.html" # gh-pages branch...

layers_csv <- readr::read_csv(file.path(
  "https://raw.githubusercontent.com/OHI-Science/bhi-1.0-archive/draft/",
  "baltic2015",
  "layers.csv")) # need to read from github so works in eg  ghpages branch
st0 <- layers_csv %>%
  select(targets, name, layer, description) %>% 
  filter(name != "proxy_layer") %>% 
  mutate(description = ifelse(is.na(description), "See goal description above or data prep documents for more information.", description)) %>% 
  
  mutate(description = str_remove_all(description, pattern = "\\n\\n\\n\\n-")) %>% 
  mutate(
    name_abbrev = name %>% 
      str_replace_all(pattern = "\\(", replacement = "openparentheses ") %>% 
      str_replace_all(pattern = "\\.", replacement = " periodpunctuation") %>% 
      str_replace_all(pattern = "to be used", replacement = "tobeused") %>% 
      str_replace_all(pattern = "based on|based upon", replacement = "basedon")
  ) %>%
  rowwise() %>% 
  mutate(
    name_abbrev = ifelse(
      str_length(name) < 35,
      name,
      str_split(
        name_abbrev,
        pattern = paste0("\\s", 
          intersect(
             c("openparentheses", "periodpunctuation", ",", "basedon", "tobeused", "as", "of"),
            str_split(name_abbrev, pattern = " ") %>% unlist())[1], "\\s"
        )
      )[[1]][1]
    )
  ) %>%
  mutate(
    web_name = str_to_lower(gsub(" ", "_", name_abbrev)) %>% 
      gsub(pattern = "/", replacement = "")
  ) %>% 
  
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name_abbrev, layers_web, web_name, layer, description))

prs_matrix <- readr::read_csv(file.path(dir_assess, "conf", "pressures_matrix.csv"))
res_matrix <- readr::read_csv(file.path(dir_assess, "conf", "resilience_matrix.csv"))
```


## Food Provision: Fisheries
<br>

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "FIS.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-1.0-archive/blob/draft/baltic2015/prep/FIS/fis_np_prep.md)  

### Data used in model

**Status & trend**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "FIS")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
prs_lyr <- prs_matrix %>%
  filter(goal == "FIS") %>% 
  select_if(function(x) {!all(is.na(x))}) %>% 
  select(-goal) %>% names()

st <- filter(st0, targets %in% "pressures", layer %in% prs_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
res_lyr <- res_matrix %>%
  filter(goal == "FIS") %>% 
  select_if(function(x) {!all(is.na(x))}) %>% 
  select(-goal) %>% names()

st <- filter(st0, targets %in% "resilience", layer %in% res_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 


---- 

## Food Provision: Mariculture
<br>

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "MAR.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-1.0-archive/blob/draft/baltic2015/prep/MAR/mar_prep.md)  

### Data used in model

**Status & trend**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "MAR")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
prs_lyr <- prs_matrix %>% 
  filter(goal == "MAR") %>%
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "pressures", layer %in% prs_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
res_lyr <- res_matrix %>%   
  filter(goal == "MAR") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "resilience", layer %in% res_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 


---- 

## Artisanal Fishing Opportunity 
<br>

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "AO.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 


[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-1.0-archive/blob/draft/baltic2015/prep/AO/ao_prep.md)  

### Data used in model

**Status & trend**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "AO")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
prs_lyr <- prs_matrix %>%   
  filter(goal == "AO") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "pressures", layer %in% prs_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
res_lyr <- res_matrix %>%   
  filter(goal == "AO") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "resilience", layer %in% res_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 


---- 

## Natural Products
<br>

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "NP.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 


[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-1.0-archive/blob/draft/baltic2015/prep/NP/np_prep.md)  

### Data used in model

**Status & trend**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "NP")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
prs_lyr <- prs_matrix %>%   
  filter(goal == "NP") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "pressures", layer %in% prs_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
res_lyr <- res_matrix %>%   
  filter(goal == "NP") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "resilience", layer %in% res_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 


---- 

## Carbon Storage
<br>

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "CS.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-1.0-archive/blob/draft/baltic2015/prep/CS/cs_prep.md)  

### Data used in model

**Status & trend**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "CS")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
prs_lyr <- prs_matrix %>%   
  filter(goal == "CS") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "pressures", layer %in% prs_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
res_lyr <- res_matrix %>%   
  filter(goal == "CS") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names() 

st <- filter(st0, targets %in% "resilience", layer %in% res_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 

---- 

## Tourism & Recreation
<br>

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "TR.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-1.0-archive/blob/draft/baltic2015/prep/TR/tr_prep.md)  

### Data used in model

**Status & trend**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "TR")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
prs_lyr <- prs_matrix %>%   
  filter(goal == "TR") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "pressures", layer %in% prs_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
res_lyr <- res_matrix %>%   
  filter(goal == "TR") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "resilience", layer %in% res_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 

---- 

## Livelihoods & Economies: Livelihoods
<br>

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "LIV.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-1.0-archive/blob/draft/baltic2015/prep/LIV/liv_prep.md)  

### Data used in model

**Status & trend**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "LIV")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
prs_lyr <- prs_matrix %>%   
  filter(goal == "LIV") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "pressures", layer %in% prs_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
res_lyr <- res_matrix %>%   
  filter(goal == "LIV") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "resilience", layer %in% res_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 


---- 

## Livelihoods & Economies: Economies
<br>

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "ECO.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-1.0-archive/blob/draft/baltic2015/prep/ECO/eco_prep.md)  

### Data used in model

**Status & trend**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "ECO")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
prs_lyr <- prs_matrix %>%   
  filter(goal == "ECO") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "pressures", layer %in% prs_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
res_lyr <- res_matrix %>%   
  filter(goal == "ECO") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "resilience", layer %in% res_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 

---- 

## Sense of Place: Iconic Species
<br>

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "ICO.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-1.0-archive/blob/draft/baltic2015/prep/ICO/ico_prep.md)  

### Data used in model

**Status & trend**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "ICO")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
prs_lyr <- prs_matrix %>% 
  filter(goal == "ICO") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "pressures", layer %in% prs_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
res_lyr <- res_matrix %>%   
  filter(goal == "ICO") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "resilience", layer %in% res_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 


---- 

## Sense of Place: Lasting Special Places
<br>

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "LSP.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-1.0-archive/blob/draft/baltic2015/prep/LSP/lsp_prep.md)  

### Data used in model

**Status & trend**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "LSP")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
prs_lyr <- prs_matrix %>%   
  filter(goal == "LSP") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "pressures", layer %in% prs_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
res_lyr <- res_matrix %>%   
  filter(goal == "LSP") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "resilience", layer %in% res_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 


---- 

## Clean Waters: Eutrophication
<br>

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "EUT.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-1.0-archive/blob/draft/baltic2015/prep/CW/eutrophication/eutrophication_prep.md)  

### Data used in model

**Status & trend**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "EUT")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
prs_lyr <- prs_matrix %>%   filter(goal == "EUT") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "pressures", layer %in% prs_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
res_lyr <- res_matrix %>%   
  filter(goal == "EUT") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "resilience", layer %in% res_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 


---- 

## Clean Waters: Trash
<br>

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "TRA.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-1.0-archive/blob/draft/baltic2015/prep/CW/trash/tra_prep.md)  

### Data used in model

**Status & trend**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "TRA")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
prs_lyr <- prs_matrix %>%   
  filter(goal == "TRA") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "pressures", layer %in% prs_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
res_lyr <- res_matrix %>%   
  filter(goal == "TRA") %>%   
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "resilience", layer %in% res_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 


---- 

## Clean Waters: Contaminants
<br>

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "CON.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-1.0-archive/blob/draft/baltic2015/prep/CW/contaminants/contaminants_prep.md)  

### Data used in model

**Status & trend**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "CON")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
prs_lyr <- prs_matrix %>%   
  filter(goal == "CON") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "pressures", layer %in% prs_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
res_lyr <- res_matrix %>%   
  filter(goal == "CON") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names() 

st <- filter(st0, targets %in% "resilience", layer %in% res_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 


---- 

## Biodiversity
<br>

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "BD.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-1.0-archive/blob/draft/baltic2015/prep/SPP/spp_prep.md)  

### Data used in model

**Status & trend**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "BD")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
prs_lyr <- prs_matrix %>%   
  filter(goal == "BD") %>%  
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names() 

st <- filter(st0, targets %in% "pressures", layer %in% prs_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**

```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
res_lyr <- res_matrix %>%   
  filter(goal == "BD") %>%    
  select_if(function(x) {!all(is.na(x))}) %>%    
  select(-goal) %>% names()  

st <- filter(st0, targets %in% "resilience", layer %in% res_lyr)
cat(paste(st$info, collapse = "\n\n"))
``` 

