---
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
## this document links to the bhi-prep github repo, using 
layers_web <- "http://ohi-science.org/bhi/data.html" # gh-pages branch...
# short_goal_web <- file.path(bhiprep_gh_raw, "conf", "goals") # bhiprep_gh_raw defined in setup.R  
short_goal_web <- file.path(
  "https://raw.githubusercontent.com/OHI-Science/bhi-1.0-archive",
  "draft/baltic2015", 
  "conf", "web", "goals"
)

layers_csv <- readr::read_csv(file.path(dir_baltic, "layers.csv"))
st0 <- layers_csv %>%
  select(targets, name, layer, description) %>% 
  mutate(web_name = str_to_lower(gsub(" ", "_", name))) %>% 
  mutate(web_name = gsub("/", "", web_name)) %>% 
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))
```


## Food Provision: Fisheries

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "FIS.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-prep/blob/master/prep/FIS/v2019/fis_np_prep.rmd)  

### Data used in model

**Status & trend**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "FIS")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "pressures")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "resilience")
cat(paste(st$info, collapse = "\n\n"))
``` 


---- 

## Food Provision: Mariculture

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "MAR.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-prep/blob/master/prep/MAR/v2019/mar_prep.rmd)  

### Data used in model

**Status & trend**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "MAR")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "pressures")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "resilience")
cat(paste(st$info, collapse = "\n\n"))
``` 


---- 

## Artisanal Fishing Opportunity 

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "AO.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 


[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-prep/blob/master/prep/AO/v2019/ao_prep.rmd)  

### Data used in model

**Status & trend**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "AO")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "pressures")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "resilience")
cat(paste(st$info, collapse = "\n\n"))
``` 


---- 

## Natural Products

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "NP.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 


[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-prep/blob/master/prep/NP/v2019/np_prep.rmd)  

### Data used in model

**Status & trend**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "NP")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "pressures")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "resilience")
cat(paste(st$info, collapse = "\n\n"))
``` 


---- 

## Carbon Storage

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "CS.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-prep/blob/master/prep/CS/v2019/cs_prep.rmd)  

### Data used in model

**Status & trend**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "CS")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "pressures")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "resilience")
cat(paste(st$info, collapse = "\n\n"))
``` 

---- 

## Tourism & Recreation

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "TR.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-prep/blob/master/prep/TR/v2019/tr_prep.rmd)  

### Data used in model

**Status & trend**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "TR")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "pressures")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "resilience")
cat(paste(st$info, collapse = "\n\n"))
``` 

---- 

## Livelihoods & Economies: Livelihoods

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "LIV.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-prep/blob/master/prep/LIV/v2019/liv_prep.rmd)  

### Data used in model

**Status & trend**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "LIV")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "pressures")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "resilience")
cat(paste(st$info, collapse = "\n\n"))
``` 


---- 

## Livelihoods & Economies: Economies

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "ECO.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-prep/blob/master/prep/ECO/v2019/eco_prep.rmd)  

### Data used in model

**Status & trend**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "ECO")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "pressures")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "resilience")
cat(paste(st$info, collapse = "\n\n"))
``` 

---- 

## Sense of Place: Iconic Species

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "ICO.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-prep/blob/masterNA.rmd)  

### Data used in model

**Status & trend**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "ICO")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "pressures")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "resilience")
cat(paste(st$info, collapse = "\n\n"))
``` 


---- 

## Sense of Place: Lasting Special Places

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "LSP.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-prep/blob/master/prep/LSP/v2019/lsp_prep.rmd)  

### Data used in model

**Status & trend**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "LSP")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "pressures")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "resilience")
cat(paste(st$info, collapse = "\n\n"))
``` 


---- 

## Clean Waters: Eutrophication

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "EUT.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-prep/blob/master/prep/CW/eutrophication/v2019/eutrophication_prep.rmd)  

### Data used in model

**Status & trend**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "EUT")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "pressures")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "resilience")
cat(paste(st$info, collapse = "\n\n"))
``` 


---- 

## Clean Waters: Trash

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "TRA.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-prep/blob/master/prep/CW/trash/v2019/tra_prep.rmd)  

### Data used in model

**Status & trend**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "TRA")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "pressures")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "resilience")
cat(paste(st$info, collapse = "\n\n"))
``` 


---- 

## Clean Waters: Contaminants

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "CON.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-prep/blob/master/prep/CW/contaminants/v2019/contaminants_prep.rmd)  

### Data used in model

**Status & trend**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "CON")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "pressures")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "resilience")
cat(paste(st$info, collapse = "\n\n"))
``` 


---- 

## Biodiversity

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_goal_web, "BD.Rmd"), tmp) 
```
 
```{r, child = tmp, echo = FALSE, results = "asis"} 
``` 

[**Full data preparation information and code**](https://github.com/OHI-Science/bhi-prep/blob/master/prep/SPP/v2019/spp_prep.rmd)  

### Data used in model

**Status & trend**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "BD")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Pressure**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "pressures")
cat(paste(st$info, collapse = "\n\n"))
``` 

**Resilience**
```{r, echo = FALSE, warning = FALSE, error = FALSE, results = "asis"}
st <- filter(st0, targets %in% "resilience")
cat(paste(st$info, collapse = "\n\n"))
``` 

