---
output:
  html_document:
    toc: true
    toc_float: true
---

<!-- keep this top  'setup' chunk with the line underneath but delete the rest if regenerating/updating from 'make_layer_summaries' script -->

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
source(file.path(here::here(), "R", "setup.R"))
short_layer_web <- file.path(bhiprep_gh_raw, "master", "ref", "layer_summaries") # bhiprep_gh_raw defined in setup.R
```

---

<!-- delete anything below hereif regenerating/updating from 'make_layer_summaries' script  -->
## Slope Of Coastal Fish Stocks To Be Used For Trend

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "ao_stock_slope.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Status Of Coastal Fish Stocks

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "ao_stock_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Bd Status Based On Species Biodiversity. Based On Geometric Mean Of Taxa Group Status.

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "bd_spp_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Bd Trend Taken From Ohi-Global 2016 For Baltic Countries

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "bd_spp_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Ocean Acidification

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cc_acid.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Current Deep Water Salinity (Depth Varies By Basin) Rescaled Between Historic Max And Future Min

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cc_sal_deep.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Current Surface Salinity Water Rescaled Between Historic Max And Future Min

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cc_sal_surf.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Sea Level Rise

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cc_slr.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Sea Surface Temperature

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cc_sst.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Uv Radiation

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cc_uv.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Status Of Cs

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cs_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Chemical Pollution Trend

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_chemical_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Status Of Dioxin And Dioxin-Like Pcb Indicator. Helcom And Eu Human Health Threshold Used.

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_con_dioxin_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Trend  Of Dioxin And Dioxin-Like Pcb Indicator.  Helcom And Eu Human Health Threshold Used.

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_con_dioxin_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Status Of Ices6 Con Indicator Based On The Ices6 Pcbs. Helcom And Eu Human Health Threshold Used

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_con_ices6_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Trend Of Ices6 Con Indicator Based On The Ices6 Pcbs. Helcom And Eu Human Health Threshold Used

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_con_ices6_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Penalty Factor For Con

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_con_penalty.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Status Of Pfos Contaminants Indicator. Helcom Human Health Threshold.

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_con_pfos_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Trend Of Pfos Contaminants Indicator. Helcom Human Health Threshold.

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_con_pfos_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Status Of Eut

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_eut_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Trend Of Eut

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_eut_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Nutrient Pollution Trend

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_nutrient_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Pathogen Pollution Trend

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_pathogen_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Status Of Trash

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_tra_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Trend Of Trash

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_tra_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Plastic Trash Trends

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_trash_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Status Of Eco

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "eco_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Trend Of Eco

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "eco_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Coastal Protection Weights

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "element_wts_cp_km2_x_protection.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Carbon Storage Weights

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "element_wts_cs_km2_x_storage.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Habitat Presence/Absence

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "element_wts_hab_pres_abs.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## B/Bmsy By Stock And Year

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "fis_bbmsy.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## F/Fmsy By Stock And Year

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "fis_ffmsy.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Landings By Stock And Year

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "fis_landings.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## High Bycatch Due To Artisanal Fishing

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "fp_art_hb.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Low Bycatch Due To Artisanal Fishing

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "fp_art_lb.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## High Bycatch Due To Commercial Fishing

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "fp_com_hb.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Low Bycatch Due To Commercial Fishing

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "fp_com_lb.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Proxy_layer

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "fp_over_harvest.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Targeted Harvest Of Cetaceans And Marine Turtles

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "fp_targetharvest.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Fisheries Weighting Factor

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "fp_wildcaught_weight.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Cites Signatories

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "g_cites.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Management Of Mariculture  To Preserve Biodiversity

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "g_mariculture.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Mariculture Sustainability Index

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "g_msi_gov.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Management Of Tourism To Preserve Biodiversity

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "g_tourism.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Bottom Oxygen Level (Mg_l_1)

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_anoxia.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Proxy_layer

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_bottom_trawl.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Habitat Extent Of Coral

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_coral_extent.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Habitat Condition Of Coral

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_coral_health.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Habitat Condition Trend Of Coral

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_coral_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Proxy_layer

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_illegal_oil.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Habitat Extent Of Mangrove

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_mangrove_extent.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Habitat Condition Of Mangrove

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_mangrove_health.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Habitat Condition Trend Of Mangrove

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_mangrove_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Habitat Extent Of Rocky Reef

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_rockyreef_extent.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Habitat Extent Of Saltmarsh

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_saltmarsh_extent.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Habitat Condition Of Saltmarsh

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_saltmarsh_health.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Habitat Condition Trend Of Saltmarsh

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_saltmarsh_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Habitat Extent Of Seagrass

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_seagrass_extent.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Habitat Condition Of Seagrass

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_seagrass_health.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Habitat Condition Trend Of Seagrass

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_seagrass_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Habitat Extent Of Seaice

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_seaice_extent.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Habitat Condition Of Seaice

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_seaice_health.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Habitat Condition Trend Of Seaice

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_seaice_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Habitat Extent Of Softbottom

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_softbottom_extent.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Habitat Condition Of Softbottom

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_softbottom_health.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Habitat Condition Trend Of Softbottom

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_softbottom_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Management Of Habitat To Protect Habitat Biodiversity

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hd_habitat.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Intertidal Habitat Destruction

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hd_intertidal.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Coastal Protected Marine Areas (Habitat Preservation)

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hd_mpa_coast.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Eez Protected Marine Areas (Habitat Preservation)

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hd_mpa_eez.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Subtidal Hardbottom Habitat Destruction

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hd_subtidal_hb.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Subtidal Soft Bottom Habitat Destruction

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hd_subtidal_sb.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Iucn Extinction Risk

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "ico_spp_iucn_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Ico Spp Status Based Upon Fish And Mammals Redlist Threat Level From Helcom

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "ico_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## National Per Capita Gdp

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "le_gdp_country.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Per Capita Gdp Per Bhi Region

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "le_gdp_region.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Sectors In Each Region

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "le_sector_weight.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Global Competitiveness Index (Gci)

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "li_gci.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Economic Diversity

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "li_sector_evenness.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Number Of People Employed Nationally Based On National Employment Rates

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "liv_national_employ.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Number Of People Employed In Each Bhi Region 25km Buffer Based On Euts2 Employment Rates

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "liv_regional_employ.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Status Of Livelihood

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "liv_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Trend Of Livelihood

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "liv_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Inland Coastal Protected Areas

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "lsp_prot_area_inland1km.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Offshore Coastal Protected Areas

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "lsp_prot_area_offshore3nm.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Status Scores Of Lsp

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "lsp_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Trend Of Lsp

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "lsp_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Inland Coastal Population

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "mar_coastalpopn_inland25mi.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Mariculture Species Harvested

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "mar_harvest_species.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Mariculture Harvest

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "mar_harvest_tonnes.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Mariculture Sustainability Score

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "mar_sustainability_score.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## B/Bmsy By Stock And Year Of Sprat

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "np_bbmsy.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Blast Fishing

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "np_blast.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Poison Fishing

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "np_cyanide.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## F/Fmsy By Stock And Year Of Sprat

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "np_ffmsy.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Relative Natural Product Harvest Value

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "np_harvest_product_weight.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Natural Product Harvest

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "np_harvest_tonnes.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Relative Natural Product Harvest Tonnes

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "np_harvest_tonnes_relative.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Landings By Stock And Year Of Sprat

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "np_landings.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Atmospheric Deposition Of Pcb 153 To The Baltic Sea

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "po_atmos_pcb153.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Chemical Pollution

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "po_chemicals.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Coastal Chemical Pollution

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "po_chemicals_3nm.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Water Clarity / Transparency Pressure

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "po_inverse_secchi.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Nitrogen Pollution

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "po_nload.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Nutrient Pollution

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "po_nutrients.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Coastal Nutrient Pollution

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "po_nutrients_3nm.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Pathogen Pollution

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "po_pathogens.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Phosphorus Pollution

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "po_pload.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Marine Plastics

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "po_trash.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Management Of Waters To Preserve Biodiversity

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "po_water.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Proxy_layer

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_biodiversity.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Directive 2009/147/Ec Of The European Parliament And Of The Council Of 30 November 2009 On The Conservation Of Wild Birds

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_birds.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Helcom 2007. Helcom Baltic Sea Action Plan (Bsap). Helcom Ministerial Meeting. Adopted In Krakow, Poland, 15 November 2007.

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_bsap.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Directive 2006/7/Ec Of The European Parliament And Of The Council Of 15 February 2006 Concerning The Management Of Bathing Water Quality And Repealing The Directive 76/160/Ec

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_bwd.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Convention On Biodiversity

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_cbd.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Regulation 1380/2013/Eu Of The European Parliament And Of The Council Of 11 December 2013 On The Common Fisheries Policy, Amending Council Regulations (Ec) No 1954/2003 And (Ec) No 1224/2009 And Repealing Council Regulations (Ec) No 2371/2002 And (Ec) No

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_cfp.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Convention On International Trade In Endangered Species Of Wild Fauna And Flora

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_cites.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Paris Climate Agreement

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_cop21.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Directive 1992/43/Ec Of 21 May 1992 On The Conservation Of Natural Habitats And Of Wild Fauna And Flora

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_hd.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Convention On The Protection Of The Marine Environment Of The Baltic Sea Area 1992

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_helcom.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Directive 2010/75/Eu Of The European Parliament And Of The Council Of 24 November 2010 On Industrial Emissions (Integrated Pollution Prevention And Control)

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_ied.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Directive 2008/56/Ec Of The European Parliament And Of The Council Of 17 June 2008 Establishing A Framework For Community Action In The Field Of Marine Environmental Policy

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_msfd.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Directive 2014/89/Ec Of The European Parliament And Of The Council Of 23 July 2014 Establishing A Framework For Maritime Spatial Planning

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_mspd.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Council Directive 91/676/Eec Of 12 December 1991 Concerning The Protection Of Waters Against Pollution Caused By Nitrates From Agricultural Sources

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_nd.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Directive 1999/32/Ec Of 26 April 1999 Relating To A Reduction In The Sulphur Content Of Certain Liquid Fuels And Amending Directive 93/12/Eec

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_nec.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Regulation 850/2004/Ec Of The European Parliament And Of The Council Of 29 April 2004 On Persistent Organic Pollutants And Amending Directive 79/117/Eec

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_pop.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Regulation 1907/2006/Ec Of The European Parliament And Of The Council Of 18 December 2006 Concerning The Registration, Evaluation, Authorisation And Restriction Of Chemicals (Reach), Establishing A European Chemicals Agency, Amending Directive 1999/45/Ec

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_reach.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Directive 1991/271/Eec Council Directive Of 21 May 1991 Concerning Urban Waste Water Treatment

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_uwwtd.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Directive 2000/60/Ec Of The European Parliament And Of The Council Of 23 October 2000 Establishing A Framework For Community Action In The Field Of Water Policy

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_wfd.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Social Progress Index

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_spi.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Region Areas Based On Eez Boundaries

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "rgn_area.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Inland 1km Area

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "rgn_area_inland1km.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Offshore 3nm Area

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "rgn_area_offshore3nm.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Ohi Region Id

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "rgn_global.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Regions

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "rgn_labels.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Nonindigenous Species

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "sp_alien.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Management Of Nonindigenous Species

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "sp_alien_species.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Genetic Escapes

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "sp_genetic.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Invasive Species Pressure Scores

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "sp_invasives.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Measure Of Coastal Ecological Integrity

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "species_diversity_3nm.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Measure Of Ecological Integrity

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "species_diversity_eez.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Average Species Condition

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "spp_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Average Species Condition Trend

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "spp_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Weakness Of Social Progress

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "ss_spi.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Weakness Of Governance

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "ss_wgi.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Total Coastal Nights In Accommodation Stays

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "tr_accommodation_stays.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Percent Direct Employment In Tourism

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "tr_jobs_pct_tourism.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Tourism And Recreation Status Scores

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "tr_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Tourism Sustainability Index

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "tr_sustainability.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Us State Department Travel Warnings

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "tr_travelwarnings.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Tourism And Recreation Trend Scores

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "tr_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Uninhabited Regions

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "uninhabited.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

## Strength Of Governance

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "wgi_all.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

