---
output:
  html_document:
    toc: true
    toc_float: true
---

<!-- keep this top  'setup' chunk with the line underneath but delete the rest if regenerating/updating from 'make_layer_summaries' script -->

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
source(file.path(here::here(), "R", "setup.R"))
short_layer_web <- file.path(bhiprep_gh_raw, "master", "ref", "layer_summaries") # bhiprep_gh_raw defined in setup.R
```

---

<!-- delete anything below hereif regenerating/updating from 'make_layer_summaries' script  -->
### Slope Of Coastal Fish Stocks

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "ao_stock_slope.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Status Of Coastal Fish Stocks

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "ao_stock_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Bd Statusbased On Species Biodiversity

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "bd_spp_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Bd Trend Taken From Ohi-Global 2016 For Baltic Countries

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "bd_spp_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Current Deep Water Salinity

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cc_sal_deep.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Current Surface Salinity Water Rescaled Between Historic Max And Future Min

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cc_sal_surf.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Current Sea Surface Temperature

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cc_sst.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Status Of Cs

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cs_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Coastal Human Population

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_coastalpopn_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Status Of Dioxin And Dioxin-Like Pcb Indicator

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_con_dioxin_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Trend  Of Dioxin And Dioxin-Like Pcb Indicator

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_con_dioxin_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Status Of Ices6 Con Indicatorbased On The Ices6 Pcbs

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_con_ices6_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Trend Of Ices6 Con Indicatorbased On The Ices6 Pcbs

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_con_ices6_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Penalty Factor For Con

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_con_penalty.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Status Of Pfos Contaminants Indicator

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_con_pfos_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Trend Of Pfos Contaminants Indicator

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_con_pfos_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Status Of Eut

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_eut_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Trend Of Eut

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_eut_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Status Of Trash

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_tra_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Trend Of Trash

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "cw_tra_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Status Of Eco

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "eco_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Trend Of Eco

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "eco_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### B/Bmsy By Stock And Year

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "fis_bbmsy.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### F/Fmsy By Stock And Year

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "fis_ffmsy.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Landings By Stock And Year

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "fis_landings.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Fisheries Weighting Factor

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "fp_wildcaught_weight.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Bottom Oxygen Level (Mg_l_1)

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "hab_anoxia.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Ico Spp Status

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "ico_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### National Per Capita Gdp

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "le_gdp_country.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Per Capita Gdp Per Bhi Region

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "le_gdp_region.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Number Of People Employed Nationally

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "liv_national_employ.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Number Of People Employed In Each Bhi Region 25km Buffer

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "liv_regional_employ.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Status Of Livelihood

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "liv_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Trend Of Livelihood

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "liv_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Status Scores Of Lsp

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "lsp_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Trend Of Lsp

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "lsp_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Coastal Population Inland 25 Kilometers

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "mar_coastalpopn2005_inland25km.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Mariculture Species Harvested

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "mar_harvest_species.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Mariculture Harvest

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "mar_harvest_tonnes.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Mariculture Sustainability Score

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "mar_sustainability_score.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### B/Bmsy By Stock And Year Of Sprat

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "np_bbmsy.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### F/Fmsy By Stock And Year Of Sprat

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "np_ffmsy.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Landings By Stock And Year Of Sprat

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "np_landings.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Atmospheric Deposition

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "po_atmos_pcb153.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Atmospheric Deposition

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "po_atmos_pcddf.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Water Clarity / Transparency Pressure

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "po_inverse_secchi.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Nitrogen Pollution

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "po_nload.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Phosphorus Pollution

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "po_pload.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Trash Pollution

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "po_trash.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Directive 2009/147/Ec

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_birds.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Helcom 2007. Helcom Baltic Sea Action Plan

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_bsap.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Directive 2006/7/Ec

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_bwd.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Convention On Biodiversity

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_cbd.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Regulation 1380/2013/Eu

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_cfp.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Convention On International Trade In Endangered Species

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_cites.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Paris Climate Agreement

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_cop21.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Directive 1992/43/Ec

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_hd.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Convention On The Protection

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_helcom.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Directive 2010/75/Eu

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_ied.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Directive 2008/56/Ec

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_msfd.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Directive 2014/89/Ec

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_mspd.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Council Directive 91/676/Eec

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_nd.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Directive 1999/32/Ec

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_nec.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Regulation 850/2004/Ec

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_pop.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Regulation 1907/2006/Ec

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_reach.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Directive 1991/271/Eec Council Directive

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_uwwtd.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Directive 2000/60/Ec

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "res_reg_wfd.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Region Area Of Total Eez Ocean

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "rgn_area.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Region Area 1 Km Inland

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "rgn_area_inland1km.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Region Area Offshore 3nm

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "rgn_area_offshore3nm.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Georegion Labels Per Region, At 3 Georegion Levels

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "rgn_georegion_labels.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Georegion Ids Per Region, At 3 Georegion Levels

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "rgn_georegions.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Regions Used In Global Analysis For Nature 2012, Subset

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "rgn_global.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Regions By Type

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "rgn_labels.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Invasive Species Pressure Scores

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "sp_invasives.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Weakness Of Governance Indicated With The Wgi

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "ss_wgi.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Total Coastal Nights In Accommodation Stays

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "tr_accommodation_stays.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Tourism And Recreation Status Scores

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "tr_status.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Tourism And Recreation Trend Scores

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "tr_trend.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

### Strength Of Governance Indicated With The Wgi

```{r, echo = FALSE, results = "hide"}
tmp <- tempfile(fileext = "Rmd")
on.exit(unlink(tmp))
download.file(file.path(short_layer_web, "wgi_all.Rmd"), tmp)
```

```{r, child = tmp, echo = FALSE, results = "asis"}
```

---

