---
title: "Calculate OHI scores"
output: html_document
---

R code to calculate BHI scores using the `ohicore` package.

----
## Install R packages

Run this code chunk one time only to install packages you don't already have. This is like wiring a building for electricity.

```{r install packages, eval=FALSE}
## install packages from R community
install.packages("tidyverse")
install.packages("zoo")
install.packages("here")
install.packages("devtools")

## install the ohicore package from OHI team
devtools::install_github("ohi-science/ohicore")
```

## Load R packages

Run this every time you calculate scores so that you will have libraries available to you. This is like turning on the lights in a building. Additionally, you will set the working directory to your scenario folder. The syntax `::` identifies which library a function is from.

```{r setup, eval=FALSE}
## load package libraries
library(tidyverse)
library(stringr)
library(zoo)
library(here)
library(ohicore)
library(httr)

## set the working directory to a filepath we all have
setwd(here::here("baltic"))

## source common.R
source("../R/common.R")

## identify the repository that data layers will be taken from
repo_loc <- "https://raw.githubusercontent.com/OHI-Science/bhi-prep/master"

## at this point, double check that all bhi-prep changes have been pushed to github!
```

## Configure Toolbox

Run this chunk each time you calculate scores to ensure that all files in your repo are properly configured. These functions from ohicore (`ohicore::`) will check your repo's files to make sure you have registered layers properly, etc. It will create `conf` and `layers` objects that will be used to calculate scores. *Note: you must re-run this code chunk before calculating scores if you have made changes to functions.R, goals.csv, etc*. These functions will not modify layers files.

```{r configure toolbox, eval=FALSE}
## copy layers over from the bhi-prep repository
assessment_path <- getwd() # working dir was set to 'baltic' above

## copy the layers for the assessment from the bhi-prep repository 'layers' folder
copy_layers_for_assessment(assessment_path, repo_loc)

## scenario years in this year's assessment
scenario_years <- c(2015, 2016)
```

## Calculate and save scores

Run this chunk to calculate and save scores as `scores` object and as `scores.csv`. You can examine `scores.csv` in the Git tab of RStudio to explore what changed. This chunk uses a function `calculate_scores` which can be found in `bhi/R/common.R`.

```{r calculate scores, eval=FALSE}
## calculate scores for all scenario years and save as scores.csv
calculate_scores(assessment_path, scenario_years, scores_path = ".")
```



<!-- ## Create figures -->

<!-- Run this to create flower plots for each region. -->

<!-- ```{r plot, eval=FALSE} -->
<!-- ## source script (to be incorporated into ohicore) -->
<!-- source("https://raw.githubusercontent.com/OHI-Science/arc/master/circle2016/plot_flower_local.R") -->

<!-- PlotFlower(assessment_name = "Baltic", dir_fig_save = "reports/figures") -->
<!-- ``` -->

