---
title: "Calculate OHI scores"
output: html_document
---

R code to calculate BHI scores using the `ohicore` package.

----
## Install R packages

Run this code chunk one time only to install packages you don't already have. This is like wiring a building for electricity.

```{r install packages, eval=FALSE}
## install packages from R community
install.packages("tidyverse")
install.packages("zoo")
install.packages("here")
install.packages("devtools")
install.packages("httr")
install.packages("tools")
install.packages("tibble")

## install the ohicore package from OHI team
devtools::install_github("ohi-science/ohicore")
```

## Load R packages

Run this every time you calculate scores so that you will have libraries available to you. This is like turning on the lights in a building. Additionally, you will set the working directory to your scenario folder. The syntax `::` identifies which library a function is from. 

```{r setup, eval=FALSE}
## source common.R, setup.R, calculating.R to load libraries, identify directories and functions
## github or directory paths can be revised in the setup.R script
source(file.path(here::here(), "R", "setup.R"))
source(file.path(here::here(), "R", "common.R"))

## set the working directory to a filepath we all have, dir_assess set in setup.R
setwd(dir_assess)

## at this point, double check that all bhi-prep changes have been pushed to github!
## make sure files in bhi-prep 'layers' folder are the ones we want for calculating scores!
```

## Configure Toolbox

Run this chunk each time you calculate scores to ensure that all layer files in your repo are up-to-date.

```{r configure toolbox, eval=FALSE}
source(file.path(here::here(), "R", "reconfiguring.R"))

## read layers.csv so proper layers can be copied from bhi-prep
lyrs <- readr::read_csv(file.path(dir_assess, "layers.csv"))

## copy layers from the bhi-prep, via gh master branch, assessment-specific layer folder
## 'copy_lyrs_from_bhiprep' function defined in reconfiguring.R
copy_lyrs_from_bhiprep(dir_assess, copy_layers = list(lyrs$filename))

## scenario years in this year's assessment
scenario_years <- 2008:2014
```

## Calculate and save scores

Run this chunk to calculate and save scores as `scores` object and as `scores.csv`. Functions from ohicore (`ohicore::`) will check your repo's files to make sure you have registered layers properly, etc. It will create `conf` and `layers` objects that will be used to calculate scores, based on current `functions.R`, `layers.csv`, etc. These functions will not modify layers files.

```{r calculate scores, eval=FALSE}
## calculate scores for all scenario years and save as scores.csv
source(file.path(here::here(), "R", "calculating.R"))
calculate_scores(dir_assess, scenario_years)
```
