---
title: "Example Scenario Testing"
output: html_document
---

**This document will have name matching the folder it is in, which is dedicated to a single specific testing scenario**
**Other files in the folder include: README, test_functions.csv**


## Description

Pretty detailed description of what this test is all about, what kinds of data we're going to test and why. Any variations in parameters, summary of alternate data preparation, links to documentation of alternative data prep, and visualiations.

```{r example of some test we did in data prep}

```



## Running Calculations

```{r configuring test and calculating alternative scores}

source(sprintf("%s/R/testing.R", here::here()))

assessment_path <- sprintf("%s/baltic", here::here())
configure_functions(assessment_path) # write functions to use into functions.R
sink() # stop sinking...

test_layers <- sprintf("%s/testing/alt_layers_full_table.csv", assessment_path)

prep_path <- file.path("GitHub/bhi-prep/baltic2019")
configure_layers(assessment_path, prep_path)

## calculate scores routine...
conf <- ohicore::Conf('conf')
ohicore::CheckLayers('layers.csv', 'layers', flds_id=conf$config$layers_id_fields)
layers <- ohicore::Layers(sprintf("%s/layers.csv", assessment_path),
                          sprintf("%s/layers", assessment_path))
scenario_years <- 2018
layers$data$scenario_year <- scenario_years








```
