---
title: "Example Testing"
output: html_document
---

**Name of this RMarkdown file will match the name of the folder it is in, dedicated to a single specific scenario**

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
source(file.path(here::here(), "R", "testing.R")) # testing.R sources common.R which creates dir_baltic
setwd(file.path(dir_baltic, "testing", "describe_test"))
```


### Summary of the Analysis

Synopsis of the _Description of the Analysis_ and _Summary of Results_ sections below.

### Rationale

Reasons we decided it was worthwhile to do this analysis.

### Description of the Analysis: Simulated Data or Alternative Model Specifications

Pretty detailed description of what this test is all about, what kinds of data we're going to test and why. Any variations in parameters, summary of alternate data preparation, links to documentation of alternative data prep, and visualiations.

```{r example of some test we did in data prep}

```

### Run Calculations

```{r configuring test and calculating alternative scores}
test_path <- getwd() # set working directory to testing subdirectory in setup code chunk
assessment_path <- bhi_baltic # testing.R sources common.R which creates dir_baltic
prep_path <- sprintf("%s%s", bhi_baltic, "-prep/prep")

test_layers <- file.path(assessment_path, "testing", "alt_layers.csv") # View(test_layers)

configure_functions(assessment_path) # write functions to use into functions.R
configure_layers(assessment_path, prep_path, test_path)

## calculate scores...
repo_loc <- "https://raw.githubusercontent.com/OHI-Science/bhi-prep/master"
copy_layers_for_assessment(assessment_path, repo_loc)
calculate_scores(assessment_path, c(2015, 2018), scores_path = getwd())
```

### Visualization and Exploration or Results

### Summary of Results

